Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-18 review_article.Rmd
start editing public face section

A grey literature review conducted by (ref) identified 33 publically available cancer atlases published on the internet between 01/01/2010 to 11/11/2015.

All the maps identified in this review were chloropleth maps, in which the representation of the map geometry stayed true to the underlying geography.

<!-- Could be nice to insert a grid of the different maps. Or at least one or two full maps -->

>>>>

A grey literature review conducted by (ref) identified 33 publically available cancer atlases published on the internet between 01/01/2010 to 11/11/2015. Reflecting the high use of chloropleth maps founds in the literature, outlined in the section above, all the public facing maps identified in this review were also chloropleth maps.
